Preliminary Thesis Defence

### 2014-01-06 bitattack.tex
updates from chromebook
spelling

\begin{refsection}
\chapter{Bitcoin Attacks: Or How Cryptocurrencies Gain Momentum}
\label{bitatt}
\vspace{\stretch{1}}
\section*{Abstract}
In this chapter I set out the idea of employing the models used for currency attacks,
to analyse how cryptocurrencies gain momentum.
Additionaly, I discuss how inflation in the cryptocurrency economy is possible.
\pagebreak

\section{Introduction}
As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies.
The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}.
However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed.
All of these cryptocurrencies are based to a large extend on the Bitcoin protocol,
but often introduce small technological innovations.

The most known of all of these alternative crypocurrencies is Litecoin. Litecoin introduces a number of small technological innovations,
the most import of these is the change that the process of `mining' coins is 4 times faster,
this has two consequences, transactions are approved faster than in the bitcoin protocol.
It also means that the technological limit for the total number of Litecoins ever available is 4x times higher.
For Bitcoin the technical limit is around 21 million Bitcoin, which is expected to be reached in the year 2140.
For Litecoin, the limit is around 84 million bitcoin, which is also expected to be reached around this time.

The key thing to note here is the perspective of the new cryptocurrecy adopt.
Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer.
The lower valued new cryptocurrency is technologically superior and thus more attractive.
Most new cryptocurrencies do not gain momentum and their value is only trivialy more than zero.
However, some currencies have gain momentum,
the previously mentioned litecoin introduces a technological innovation and build it base on that.
However, recently a new cryptocurrency has arisen and become quite popular.
This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty.
Dogecoin is a reference to an internet phenomenon called `Doge Meme'.
Despite the fact that `Dogecoin' does not have a real reason for being considered valuable
(in the sense that crypotocurrencies are considered valuable),
however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable.
We thus observe that from the perspective of economic and technological fundamentals,
there is a situation of multiple equilibria.

@@

On of the key selling points of the cryptocurrencies, and equally one of the key critisism of many economics
(e.g.~Paul Krugman), is that there is no inflation in a crypocurrency.
The crypocurrencies are designed specifically so that inflation eventually becomes impossible (once all coines are mined).

However, it is key here to understand the economy as a multi-cryptocurrency object.
Since creating a currency can be done at negligable cost,
and the only value of the cryptocurrency lies in its utility as a mechanism for transactions,
more cryptocurrencies will come into existance.
Especially since it is very simple for a merchant to accept several cryptocurrencies as a form of payment.
The effect of this will be that inflation in each cryptocurrency will remain as defined,
however, the cryptocurrency economy as a whole, will be able to experience inflation.

Additionaly, this partly addresses one of social critiques of Bitcoin,
namely the issue of bitcoin mining being excessively wastful.
Bitcoin mining does not produce anything of any social value (not unlike gold mining),
the higher value of bitcoin, the more computing power (and electricity) will be diverted to this.
However, in a multi-currency model, it will be more effective to mine alternative cryptocurrencies,
as these can initially be mined with relative ease.

>>>>

\begin{refsection}
\chapter{Bitcoin Attacks: Or How Cryptocurrencies Gain Momentum}
\label{bitatt}
\vspace{\stretch{1}}
\section*{Abstract}
In this chapter I set out the idea of employing the models used for currency attacks,
to analyse how cryptocurrencies gain momentum.
Additionally, I discuss how inflation in the cryptocurrency economy is possible.
\pagebreak

\section{Introduction}
As discussed in \autoref{bitremit}, there has been a new phenomenon in international finance called cryptocurrencies.
The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}.
However, soon after Bitcoin started gaining momentum, alternative cryptocurrencies where being designed.
All of these cryptocurrencies are based to a large extend on the Bitcoin protocol,
but often introduce small technological innovations.

The most known of all of these alternative cryptocurrencies is Litecoin. Litecoin introduces a number of small technological innovations,
the most import of these is the change that the process of `mining' coins is 4 times faster,
this has two consequences, transactions are approved faster than in the bitcoin protocol.
It also means that the technological limit for the total number of Litecoins ever available is 4x times higher.
For Bitcoin the technical limit is around 21 million Bitcoin, which is expected to be reached in the year 2140.
For Litecoin, the limit is around 84 million bitcoin, which is also expected to be reached around this time.

The key thing to note here is the perspective of the new cryptocurrency adopt.
Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer.
The lower valued new cryptocurrency is technologically superior and thus more attractive.
Most new cryptocurrencies do not gain momentum and their value is only trivially more than zero.
However, some currencies have gain momentum,
the previously mentioned litecoin introduces a technological innovation and build it base on that.
However, recently a new cryptocurrency has arisen and become quite popular.
This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty.
Dogecoin is a reference to an internet phenomenon called `Doge Meme'.
Despite the fact that `Dogecoin' does not have a real reason for being considered valuable
(in the sense that cryptocurrencies are considered valuable),
however, by utilising a previously existing internet phenomenon, and it's fan base, this currencies has become valuable.
We thus observe that from the perspective of economic and technological fundamentals,
there is a situation of multiple equilibria.

@@

On of the key selling points of the cryptocurrencies, and equally one of the key criticism of many economics
(e.g.~Paul Krugman), is that there is no inflation in a cryptocurrency.
The cryptocurrencies are designed specifically so that inflation eventually becomes impossible (once all coins are mined).

However, it is key here to understand the economy as a multi-cryptocurrency object.
Since creating a currency can be done at negligible cost,
and the only value of the cryptocurrency lies in its utility as a mechanism for transactions,
more cryptocurrencies will come into existence.
Especially since it is very simple for a merchant to accept several cryptocurrencies as a form of payment.
The effect of this will be that inflation in each cryptocurrency will remain as defined,
however, the cryptocurrency economy as a whole, will be able to experience inflation.

Additionally, this partly addresses one of social critiques of Bitcoin,
namely the issue of bitcoin mining being excessively wasteful.
Bitcoin mining does not produce anything of any social value (not unlike gold mining),
the higher value of bitcoin, the more computing power (and electricity) will be diverted to this.
However, in a multi-currency model, it will be more effective to mine alternative cryptocurrencies,
as these can initially be mined with relative ease.

### 2014-01-06 bitremit.tex
spelling

\begin{refsection}
\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
\label{bitremit}
\vspace{\stretch{1}}
\section*{Abstract}
In this chapter I describe the basis of cryptocurrencies, particularly Bitcoin.
I give an overview of what sources of data are available for analysis, and how these can be employed.
I propose a project which enables simple telephones or `stupid phones' to perform bitcoin transaction,
this can provide insights into the remittances that are transacted in Bitcoin.
\pagebreak

\section{Introduction}
In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC). 
This currency -the first of a group called cryptocurrencies- has the following economics features:

>>>>

\begin{refsection}
\chapter{Bitcoin and Remittances: The Potential of `Stupid Phones'}
\label{bitremit}
\vspace{\stretch{1}}
\section*{Abstract}
In this chapter I describe the basis of cryptocurrencies, particularly Bitcoin.
I give an overview of what sources of data are available for analysis, and how these can be employed.
I propose a project which enables simple telephones or `stupid phones' to perform bitcoin transaction,
this can provide insights into the remittances that are transacted in Bitcoin.
\pagebreak

\section{Introduction}
In the 2009 white paper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC). 
This currency -the first of a group called cryptocurrencies- has the following economics features:

### 2014-01-06 endnotes.tex
spelling

% The replication of Surviving Andersonville is already completed in term of the replication in Stata.
% We would like to redo the analysis in R \parencite{R}.
% The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
% The findings of this replication can summarised as:

%\begin{quote}
%``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R. It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data). This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
%\end{quote}

% We do not expect to find anything similar to Bell and Miller,
% but think that it can nevertheless be interesting to replicate findings using a different software package.
% In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
% In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.

The discussion of \textcite{morris1998unique} is in a very early stage.
I have looked at the paper in detail, I have also done a brief analysis of my main critique,
namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.

Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin. I would like to analyse the spread of this. I propose to follow the spread of applications for platforms which are popular in developing economies.

@@

Firstly, I was in charge of setting up a baseline diagnostic into security perceptions in Conakry, Guinea. This diagnostic will be used to analyse the impact of a police reform conducted here. The reform constitutes of the implementation of a model of `police de proximitee'. The baseline consist of 4500 interviews using smartphones in the comune of Conkary as well a large number of interviews in N'Zerekore (east Guinea). Some time after the implementation of the police reform as follow up study will be conducted. I propose to conduct an impact evaluation using the results from the studies in which I have taken and will take part.

Secondly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy. I would like to write one paper about an issue relating to this. In particular I would like to at the effect of outliers. The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}. I would like to see how these principles affect research in development microeconomics.

>>>>

The discussion of \textcite{morris1998unique} is in a very early stage.
I have looked at the paper in detail, I have also done a brief analysis of my main critique,
namely the conflation of risk (quantifiable) and Knightian uncertainty (unquantifiable).
However, I would like to present a worked out example which demonstrates how this convolution leads to the main result of the paper.
In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.

Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potential for uncontrolled low-cost remittances using Bitcoin. I would like to analyse the spread of this. I propose to follow the spread of applications for platforms which are popular in developing economies.

@@

Firstly, I was in charge of setting up a baseline diagnostic into security perceptions in Conakry, Guinea. This diagnostic will be used to analyse the impact of a police reform conducted here. The reform constitutes of the implementation of a model of `police de proximitee'. The baseline consist of 4500 interviews using smartphones in the commune of Conakry as well a large number of interviews in N'Zerekore (east Guinea). Some time after the implementation of the police reform as follow up study will be conducted. I propose to conduct an impact evaluation using the results from the studies in which I have taken and will take part.

Secondly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy. I would like to write one paper about an issue relating to this. In particular I would like to at the effect of outliers. The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as individual behaviour \parencite{kahneman2011thinking}. I would like to see how these principles affect research in development microeconomics.

### 2014-01-06 intro.tex
updates from chromebook
spelling

\begin{itemize}
\item Additional South African Evidence on Pensions and Child Growth (\autoref{sa})
% \item Replication: Surviving Andersonville (\ref{andersonville})
\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{unc})
\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{btc})
\end{itemize}

@@

Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds upon \textcite{duflo2000child, duflo2003grandmothers}.
These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
This paper makes use of a Household Survey from 2008, 2012 and 2013. The 
urvey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
As it stands now I have analysed the data from 2008 and 2012.
The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
I will discuss this in \autoref{sa}.

% Furthermore, in \autoref{andersonville},
% together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
% We were able to replicate all results from the paper, save for a few decimal numbers,
% which we have taken to be the result of rounding errors.

% However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
% When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
% As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
% The authors however, aggregate these two.
% This leads to overstated magnitudes of the social ties of POWs.
% This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
% At this point our replication is quite complete.
% Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.

@@

Lastly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
Bitcoin transactions are conducted using an electronic process called signing.
I would like to study the role of Bitcoin in remittances.
For this I would like to participate in building Bitcoin applications for the type of simple phones common in developing economies (sometimes referred to a stupid phones).
We could study the spread of bitcoin by looking at the downloads of the apps from regions,
as well looking at how releasing the app in different languages evolves.

@@

Recently there has been a shift towards more replication and further analysis of previously published results. E.g. \textcite{ioannidis2005most}.

>>>>

\begin{itemize}
\item Additional South African Evidence on Pensions and Child Growth (\autoref{sa})
\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{unc})
\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{bitremit})
\end{itemize}

@@

Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds upon \textcite{duflo2000child, duflo2003grandmothers}.
These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
This paper makes use of a Household Survey from 2008, 2012 and 2013. The 
survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
As it stands now I have analysed the data from 2008 and 2012.
The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
I will discuss this in \autoref{sa}.

@@

Lastly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
Bitcoin transactions are conducted using an electronic process called signing.
I would like to study the role of Bitcoin in remittances.
For this I would like to participate in building Bitcoin applications for the type of simple phones common in developing economies (sometimes referred to a stupid phones).
We could study the spread of Bitcoin by looking at the downloads of the apps from regions,
as well looking at how releasing the app in different languages evolves.

@@
